# Black Reading Achievement

```{r Packages, echo=FALSE, message=FALSE, warning=FALSE}

#requires install.packages("pacman")
pacman::p_load(readxl, janitor, tidyverse)

```

## Alabama {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")

```

### Lower Income in Alabama {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Alabama {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alabama") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Alaska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Alaska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Alaska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Alaska") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Arizona {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Arizona {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Arizona {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arizona") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Arkansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Arkansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Arkansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Arkansas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## California {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in California {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in California {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="California") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Colorado {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Colorado {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Colorado {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Colorado") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Connecticut {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Connecticut {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Connecticut {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Connecticut") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Delaware {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Delaware {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Delaware {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Delaware") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Florida {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Florida {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Florida {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Florida") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Georgia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Georgia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Georgia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Georgia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Hawaii {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Hawaii {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Hawaii {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Hawaii") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


## Idaho {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Idaho {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Idaho {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Idaho") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Illinois {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Illinois {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Illinois {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Illinois") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Indiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Indiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Indiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Indiana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Iowa {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Iowa {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Iowa {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Iowa") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Kansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Kansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Kansas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kansas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Kentucky {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Kentucky {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Kentucky {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Kentucky") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Louisiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Louisiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Louisiana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Louisiana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Maine {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Maine {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Maine {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maine") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Maryland {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Maryland {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Maryland {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Maryland") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Massachusetts {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Massachusetts {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Massachusetts {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Massachusetts") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Michigan {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Michigan {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Michigan {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Michigan") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Minnesota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Minnesota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Boys in Minnesota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Minnesota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Mississippi {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Mississippi {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Mississippi {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Mississippi") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Missouri {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Missouri {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Missouri {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Missouri") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Montana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Montana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Montana {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Montana") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Nebraska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Nebraska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Nebraska {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nebraska") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Nevada {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Nevada {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Nevada {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Nevada") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## New Hampshire {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in New Hampshire {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in New Hampshire {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Hampshire") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## New Jersey {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in New Jersey {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in New Jersey {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Jersey") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## New Mexico {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in New Mexico {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in New Mexico {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New Mexico") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## New York {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in New York {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in New York {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="New York") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## North Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in North Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in North Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## North Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in North Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in North Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="North Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Ohio {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Ohio {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Ohio {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Ohio") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Oklahoma {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Oklahoma {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Oklahoma {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oklahoma") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Oregon {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Oregon {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Oregon {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Oregon") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Pennsylvania {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Pennsylvania {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Pennsylvania {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Pennsylvania") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Rhode Island {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Rhode Island {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Rhode Island {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Rhode Island") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## South Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in South Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in South Carolina {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Carolina") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## South Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in South Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in South Dakota {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="South Dakota") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Tennessee {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Tennessee {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Tennessee {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Tennessee") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Texas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Texas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Texas {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Texas") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Utah {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Utah {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Utah {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Utah") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Vermont {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Vermont {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Vermont {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Vermont") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Washington {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Washington {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Washington {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Washington") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## West Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in West Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in West Virginia {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="West Virginia") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Wisconsin {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Wisconsin {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Wisconsin {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wisconsin") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

## Wyoming {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(215, 275) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

### Lower Income in Wyoming {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_nslp.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  filter(NSLP=="Eligible") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```


### Boys in Wyoming {-}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

read_csv('https://raw.githubusercontent.com/DavidBamat/Black-Hispanic-Achievement/main/g8r_race_eth_gen.csv') %>% 
  filter(Jurisdiction=="National public" | Jurisdiction=="Wyoming") %>%
  filter(RaceEth=="Black") %>%
  filter(Gender=="Male") %>%
  mutate(Mean = as.numeric(Mean)) %>%  
  ggplot(aes(x=as.numeric(Year), y=Mean, color=Jurisdiction)) +
  geom_errorbar(aes(ymin=Mean-(2*SE), ymax=Mean+(2*SE)), width=.2) +
  geom_line() +
  geom_point() +
  ylim(210, 265) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  ylab("Mean Achievement Estimate") +
  xlab("Year") +
  scale_x_continuous(breaks=seq(2003,2022,1)) +
    ggtitle("Grade 8 Reading") +
  theme(legend.position = "bottom") +   scale_color_discrete(name="")


```

